Deep Learning

### 2015-03-30 deepreview.tex
small changes and trying to reduce more

\addtolength{\textwidth}{2cm}
%\addtolength{\textwidth}{1cm}
\addtolength{\textheight}{2cm}
%\addtolength{\textheight}{1cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}

@@

\parskip 0.1in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

\author{Yann LeCun, Yoshua Bengio, Geoffrey Hinton}

\begin{document}

\maketitle

@@

Deep Learning allows machines that are composed of multiple processing 
layers to learn representions of data with multiple levels of abstraction.
These methods have dramatically improved the state-of-the-art
in speech recognition, object recognition, object detection,
and many other domains such as drug discovery and genommics. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to indicate how the machine should
change the weights that are used to compute the representation in each layer from
the representation in the previous layer.  Deep {\em convolutional nets}
have brought about dramatic improvements in processing
images, video, speech and audio, while {\em recurrent
  nets} have shone on sequential data such as text and
speech.
%Convolutional nets have quickly become the leading technology for image
%recognition and speech recognition, while recurrent nets are
%competitive in several natural language processing tasks, including
%language translation. 
%Combinations of recurrent and convolutional nets
%can generate good textual captions of images.

@@

% shallow linear classifiers
Many practical applications of ML use linear classifiers on top of
hand-engineered features. A two-class linear classifier computes a
weighted sum of the feature vector components. If the weighted sum is
above a threshold, the input is classified as belonging to a
particular category. Multiple classes can be handled by using multiple
two-class classifiers, each classifying one class against all
others. The learning procedure adjusts the weights of the linear
combination, for which the gradient is very easy to compute. Linear
classifiers have been widely used for many decades, starting with the
Perceptron model~\citep{Rosenblatt57}, the still-popular logistic
regression~\cite{Hastie2001}, and the linear support vector
machine~\cite{Vapnik+Chervonenkis-1964}. %{Boser92}.

@@

The idea that this could be done, and that it worked, was discovered independently by
several different groups in the 1970s and
1980s~\citep{Werbos74,Parker85,LeCun85,RHW}. It spurred a wave of interest for
neural networks, becoming quite popular in the late 1980s, but falling out of favor
between the mid 1990s until their rennaissance in the late 2000s.

@@

While the role of the convolutional layer is to detect local
conjunctions of features from the previous layer, the role of the
pooling layer is to merge semantically similar features into
one. Since the relative positions of the features forming a motif can
vary somewhat, reliably detecting the motif can be done by
coarse-graining the position of each feature. A typical pooling unit
computes the max of a local patch of units in one feature map (or in a
few feature maps). Neighboring pooling units take input from patches
that are shifted by more than one row or column, thereby reducing the
dimension of the representation and creating an {\em invariance} to
small shifts and distortions.  Two or three stages of convolution,
non-linearity, and pooling are stacked, followed by more convolutional
and fully-connected layers.  Back-propagating gradients through a
ConvNet is as simple as through a regular deep network, allowing all
the weights in all the filter banks to be trained. The error
derivative for a shared weight is just the sum the derivatives for all
the instances of that weight.

@@

The convolutional and pooling layers in ConvNets are directly inspired
by the classic notions of simple cells and complex cells in visual
neuroscience~\citep{Hubel62}, and the overall architecture is
reminiscent of the LGN-V1-V2-V4-IT hierarchy in the visual cortex 
ventral pathway~\citep{Felleman+VanEssen-1991}. When ConvNet models and
monkeys are shown the same picture, the activations of high-level
units in the ConvNet explains half the variance of random sets of 160
neurons in the monkey's
inferro-temporal cortex~\citep{cadieu-plos-2014}. ConvNets have their roots
in Fukushima's Neocognitron~\citep{fukushima-82} whose architecture
was somewhat similar but did not have an end-to-end supervised
learning algorithm such as backpropagation. 
A primitive one-dimensional convnet called a time-delay
neural net was used for the recognition of phonemes and simple 
words~\cite{WaibelIEEE,bottou-89}

There have been numerous applications of convolutional networks going
back to the early 1990s. A major early success was a bank check
reading system which was commercially deployed by AT\&T and NCR in
1994~\citep{lecun-98}. The system used a ConvNet trained jointly with
a probabilistic model that implemented language constraints. By the
late 1990s this system was reading over 10\% of all the checks in the
US. A number of ConvNet-based OCR and handwriting recognition systems
were later deployed by
Microsoft~\citep{simard-03}
including for Arabic and
Chinese~\citep{abdulkader-iwfhr-06,chellapilla-iwfhr-06a}. ConvNets
were also experimented with in the early 1990s for object detection 
in natural images, including faces and
hands~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95} and for face
recognition~\cite{lawrence-tnn-1997}.

@@

ConvNets are easily ammenable to efficient hardware implementations in
chips or Field-Programmable Gate
Arrays~\cite{boser-92,farabet-suml-11}.  A number of companies such as
NVIDIA, Mobileye, Intel, Qualcomm and Samsung are developing ConvNet
chips to enable real-time vision applications in smart phones,
cameras, robots, and self-driving cars.

@@

  Mikolov-et-al-NIPS2013,Bahdanau-et-al-ICLR2015,Sutskever-et-al-NIPS2014}.

@@

%\begin{figure}[ht]
\begin{figure}[b]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.49\linewidth]{word-embeddings.png}
\includegraphics[width=0.49\linewidth]{phrase_zoom2.png}
}
\caption{Left: Illustration of word representations learned for modeling
language, non-linearly projected to 2-D for visualization using the
t-SNE algorithm~\citep{VanDerMaaten08}. Right: 2-D representation
of phrases learned by an English-to-French encoder-decoder recurrent
neural network or RNN~\citep{Bahdanau-et-al-ICLR2015}. One can observe that
semantically similar words or sequences of words are  mapped to
nearby representations. The distributed representations of
words are obtained by using backpropagation to jointly learn 
a representation for each word and
a function that predicts a target quantity such as the next word
in a sequence (for language modeling) or a whole sequence
of translated words (for machine translation)~\citep{Bahdanau-et-al-ICLR2015,Sutskever-et-al-NIPS2014}.
}
\label{fig:word-embeddings}
\end{minipage}
}
\end{figure}

@@

Thanks to advances in their architecture~\citep{Hochreiter+Schmidhuber-1997,ElHihi+Bengio-nips8-small} 
and ways of training them~\citep{Sutskever-thesis2012,Pascanu+al-ICML2013-small}, RNNs
have been found to be very good at predicting the next character in
text~\citep{Sutskever-et-al-ICML2011} or the next word in a
sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a
time, for example, an English ``encoder'' network can be trained so
that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to) a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen from this
distribution and provided as input to the decoder network it will then
output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-ICLR2015,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

@@

%When LSTMs were first described \citep{Hochreiter+Schmidhuber-1997},
%their complexity may have been off-putting and, despite their
%impressive ability to learn very long-range temporal structure on toy
%problems, they were largely ignored until they were shown to yield
%excellent results in a cursive handwriting recognition
%competition~\citep{Graves-et-al-2009}. 
LSTM have subsequently proved to be very effective for tasks that have
sequential input.  When they use several hidden layers, they are
better than deep feedforward networks for speech
recognition~\citep{Graves-et-al-ICASSP2013} and unlike feedforward
nets they can implement an entire speech recognition system that goes
all the way from coefficents derived from the soundwave to the
sequence of characters in the transcription.  LSTMs or related forms
of gated units are also what is currently used for the encoder and
decoder networks that perform so well at machine
translation~\citep{Bahdanau-et-al-ICLR2015,Sutskever-et-al-NIPS2014}.

@@

The parallelization of large neural nets over a single GPU has
required to use ``mini-batches'' of samples over which the gradients
are averaged. The purpose of this is to saturate the GPU. But one big
unsolved question is the best way to scale up the training of very large neural
nets over multiple GPU cards across multiple machines. As of today, this
question is still unresolved.

@@

@@

We expect much of the future progress in vision to come from systems
that are trained end-to-end and combine ConvNets with RNNs that decide
where to look through reinfoercement learning. Such systems already
outperform passive vision systems~\citep{ba+mnih} at classification
tasks, but much more remains to be explored.  Combining reinforcement
learning with ConvNets has already produced impressive results in
learning to play many different video games~\citep{Mnih-et-al-2015}.
Similarly, when understanding sentences or whole documents we expect
future systems to learn strategies for selectively attending to one
part at a time~\citep{Bahdanau-et-al-ICLR2015}.

>>>>

\addtolength{\textwidth}{2.5cm}
%\addtolength{\textwidth}{1cm}
\addtolength{\textheight}{2.5cm}
%\addtolength{\textheight}{1cm}
\addtolength{\topmargin}{-1.25cm}
\addtolength{\oddsidemargin}{-1.25cm}
\addtolength{\evensidemargin}{-1.25cm}

@@

\parskip 0.085in
\parindent 0.0in
\setcounter{secnumdepth}{1}
\title{Deep Learning}

\author{Yann LeCun, Yoshua Bengio and Geoffrey Hinton}
\date{}
\begin{document}

\maketitle
\vspace*{-6mm}

@@

Deep Learning allows machines that are composed of multiple processing 
layers to learn representions of data with multiple levels of abstraction.
These methods have dramatically improved the state-of-the-art
in speech recognition, object recognition, object detection,
and many other domains such as drug discovery and genomics. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to indicate how the machine should
change the weights that are used to compute the representation in each layer from
the representation in the previous layer.  Deep {\em convolutional nets}
have brought about dramatic improvements in processing
images, video, speech and audio, while {\em recurrent
  nets} have shone on sequential data such as text and
speech.
%Convolutional nets have quickly become the leading technology for image
%recognition and speech recognition, while recurrent nets are
%competitive in several natural language processing tasks, including
%language translation. 
%Combinations of recurrent and convolutional nets
%can generate good textual captions of images.

@@

% shallow linear classifiers
Many practical applications of ML use linear classifiers on top of
hand-engineered features. A two-class linear classifier computes a
weighted sum of the feature vector components. If the weighted sum is
above a threshold, the input is classified as belonging to a
particular category. % Multiple classes can be handled by using multiple
% two-class classifiers, each classifying one class against all
% others. 
% The learning procedure adjusts the weights of the linear
% combination, for which the gradient is very easy to compute. Linear
% classifiers have been widely used for many decades, starting with the
% Perceptron model~\citep{Rosenblatt57} and the still-popular logistic
% regression~\cite{Hastie2001}.
% , and the linear support vector
% machine~\cite{Vapnik+Chervonenkis-1964}. %{Boser92}.

@@

The idea that this could be done, and that it worked, was discovered independently by
several different groups in the 1970s and
1980s~\citep{Werbos74,Parker85,LeCun85,RHW}. It spurred a wave of interest for
neural networks, becoming quite popular in the late 1980s, but falling out of favor
between the mid 1990s until their renaissance in the late 2000s.

@@

While the role of the convolutional layer is to detect local
conjunctions of features from the previous layer, the role of the
pooling layer is to merge semantically similar features into
one. Since the relative positions of the features forming a motif can
vary somewhat, reliably detecting the motif can be done by
coarse-graining the position of each feature. A typical pooling unit
computes the max of a local patch of units in one feature map (or in a
few feature maps). Neighboring pooling units take input from patches
that are shifted by more than one row or column, thereby reducing the
dimension of the representation and creating an {\em invariance} to
small shifts and distortions.  Two or three stages of convolution,
non-linearity, and pooling are stacked, followed by more convolutional
and fully-connected layers.  Back-propagating gradients through a
ConvNet is as simple as through a regular deep network, allowing all
the weights in all the filter banks to be trained. 
% The error
% derivative for a shared weight is just the sum the derivatives for all
% the instances of that weight.

@@

The convolutional and pooling layers in ConvNets are directly inspired
by the classic notions of simple cells and complex cells in visual
neuroscience~\citep{Hubel62}, and the overall architecture is
reminiscent of the LGN-V1-V2-V4-IT hierarchy in the visual cortex 
ventral pathway~\citep{Felleman+VanEssen-1991}. When ConvNet models and
monkeys are shown the same picture, the activations of high-level
units in the ConvNet explains half the variance of random sets of 160
neurons in the monkey's
inferro-temporal cortex~\citep{cadieu-plos-2014}. ConvNets have their roots
in Fukushima's Neocognitron~\citep{fukushima-82} whose architecture
was somewhat similar but did not have an end-to-end supervised
learning algorithm such as backpropagation. 
% A primitive one-dimensional convnet called a time-delay
% neural net was used for the recognition of phonemes and simple 
% words~\cite{WaibelIEEE,bottou-89}

There have been numerous applications of convolutional networks going
back to the early 1990s, starting with time-delay neural networks for
speech recognition and document reading~\citep{lecun-98}. 
The document reading system used a ConvNet trained jointly with
a probabilistic model that implemented language constraints. By the
late 1990s this system was reading over 10\% of all the checks in the
US. A number of ConvNet-based OCR and handwriting recognition systems
were later deployed by
Microsoft~\citep{simard-03}.
% including for Arabic and
% Chinese~\citep{abdulkader-iwfhr-06,chellapilla-iwfhr-06a}. 
% ConvNets
% were also experimented with in the early 1990s for object detection 
% in natural images, including faces and
% hands~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95} and for face
% recognition~\cite{lawrence-tnn-1997}.

@@

ConvNets are easily amenable to efficient hardware implementations in
chips or Field-Programmable Gate
Arrays~\cite{boser-92,farabet-suml-11}.  A number of companies such as
NVIDIA, Mobileye, Intel, Qualcomm and Samsung are developing ConvNet
chips to enable real-time vision applications in smart phones,
cameras, robots, and self-driving cars.

@@

  Mikolov-et-al-NIPS2013,Bahdanau-et-al-ICLR2015-small,Sutskever-et-al-NIPS2014}.

@@

%\begin{figure}[ht]
\begin{figure}[b]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.49\linewidth]{word-embeddings.png}
\includegraphics[width=0.49\linewidth]{phrase_zoom2.png}
}
\caption{Left: Illustration of word representations learned for modeling
language, non-linearly projected to 2-D for visualization using the
t-SNE algorithm~\citep{VanDerMaaten08}. Right: 2-D representation
of phrases learned by an English-to-French encoder-decoder recurrent
neural network or RNN~\citep{Bahdanau-et-al-ICLR2015-small}. One can observe that
semantically similar words or sequences of words are  mapped to
nearby representations. The distributed representations of
words are obtained by using backpropagation to jointly learn 
a representation for each word and
a function that predicts a target quantity such as the next word
in a sequence (for language modeling) or a whole sequence
of translated words (for machine translation)~\citep{Bahdanau-et-al-ICLR2015-small,Sutskever-et-al-NIPS2014}.
}
\label{fig:word-embeddings}
\end{minipage}
}
\end{figure}

@@

Thanks to advances in their architecture~\citep{Hochreiter+Schmidhuber-1997,ElHihi+Bengio-nips8-small} 
and ways of training them~\citep{Sutskever-thesis2012,Pascanu+al-ICML2013-small}, RNNs
have been found to be very good at predicting the next character in
text~\citep{Sutskever-et-al-ICML2011} or the next word in a
sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a
time, for example, an English ``encoder'' network can be trained so
that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to) a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen from this
distribution and provided as input to the decoder network it will then
output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-ICLR2015-small,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

@@

%When LSTMs were first described \citep{Hochreiter+Schmidhuber-1997},
%their complexity may have been off-putting and, despite their
%impressive ability to learn very long-range temporal structure on toy
%problems, they were largely ignored until they were shown to yield
%excellent results in a cursive handwriting recognition
%competition~\citep{Graves-et-al-2009}. 
LSTM have subsequently proved to be more effective than vanilla RNNs
especially when they have several layers for each time step~\citep{Graves-et-al-ICASSP2013},
enabling an entire speech recognition system that goes
all the way from acoustics to the
sequence of characters in the transcription.  LSTMs or related forms
of gated units are also what is currently used for the encoder and
decoder networks that perform so well at machine
translation~\citep{Bahdanau-et-al-ICLR2015-small,Sutskever-et-al-NIPS2014}.

@@

@@

% The parallelization of large neural nets over a single GPU has
% required to use ``mini-batches'' of samples over which the gradients
% are averaged. The purpose of this is to saturate the GPU. 
% But one big
% unsolved question is the best way to scale up the training of very large neural
% nets over multiple GPU cards across multiple machines. As of today, this
% question is still unresolved.

@@

We expect much of the future progress in vision to come from systems
that are trained end-to-end and combine ConvNets with RNNs that decide
where to look through reinforcement learning. Such systems already
outperform passive vision systems~\citep{ba+mnih} at classification
tasks, but much more remains to be explored.  Combining reinforcement
learning with ConvNets has already produced impressive results in
learning to play many different video games~\citep{Mnih-et-al-2015}.
Similarly, when understanding sentences or whole documents we expect
future systems to learn strategies for selectively attending to one
part at a time~\citep{Bahdanau-et-al-ICLR2015-small}.
